---
title: "Lab 4"
author: "Jude Sullivan"
date: "2/10/2022"
output: html_document
---

# In this lab, You will analyze data looking at the relationship between green reputation and three personality traits– compassion, intellectual curiosity, and openness to experiences. The dataset includes data from students and non-students.

```{r setup, include=FALSE}
# Load the tidyverse package

library(tidyverse)
library(dplyr)
```


```{r data}
#import data

dictionary <- readr::read_csv(here::here("data", "green_dictionary.csv"))
green_data <- readr::read_csv(here::here("data", "green_data.csv"))
```

## 1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). Is anything unusual?

```{r graphs/summaries}
#making green reputation composite variable

greenrep <- c("green1", "green2", "green3", "green4", "green5")
compassion <- c("comp1", "comp2", "comp3", "comp4", "comp5", "comp6", "comp7", "comp8", "comp9", "comp10")


green_data |> 
  rowwise() |> 
  mutate(
    id = id,
    greenrep_total = mean(c_across(green1:green5), na.rm = TRUE),
    compassion_total = mean(c_across(comp1:comp10), na.rm = TRUE),
    intelcur_total = mean(c_across(intel1:intel10), na.rm = TRUE),
    open_total = mean(c_across(open1:open10), na.rm = TRUE),
    .before = everything()
  ) |>
  head() 

#help from class 2/15
#unlist function breaks up the data and creates a large matrix basically

green_data |> 
  select(-id) |> 
  unlist() |> 
  unique()

#since we identified -99 as a value in the dataset, we can now recode

green_data <- green_data |> 
  mutate(
    across(
      -id,
           \(x) recode(x, "1" = 1, "2" = 2, "3" = 3, "4" = 4, "5" = 5, "-99" = NA_real_)
           )
  )
  
#reverse coding specific items; either look at the keying in the dictionary and write them down or select keying and filter

dictionary |> 
  filter(Keying == -1) |> 
  pull(Item)

#tedious method by running each one individually

# green_data <- green_data |> 
#   mutate(
#     green2 = recode(green2, "1"= 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1)
#   )

#mutating multiple columns at once

reversed <- c( "green2", "comp6", "comp7",  "comp8", "comp9", "comp10", "intel7", "intel8", "intel9", "intel10", "open7", "open8", "open9", "open10")

green_data <- green_data |> 
  mutate(
    across(
      all_of(reversed),
      \(x) recode(x, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1)
    )
  )

#computing total scores 

green_data <- green_data |> 
  rowwise() |> 
  mutate(
    green_total = mean(c_across(green1:green5), na.rm = TRUE),
    comp_total = mean(c_across(comp1:comp10), na.rm = TRUE),
    intel_total = mean(c_across(intel1:intel10), na.rm = TRUE),
    open_total = mean(c_across(open1:open10), na.rm = TRUE),
    .after = id
  ) |> 
  ungroup()
  
#that does not seem to work hehe

#pomping

green_data <- green_data |> 
  mutate(
    across(
      green_total:open_total,
      \(x) 100 * (x-1) / (5-1),
      .names = "{.col}_pomp"
    )
  )

#plotting

ggplot(green_data) +
  aes(x = green_total_pomp) +
  geom_histogram()

#dropping NA students and creating linear lines

green_data |> 
  filter(!is.na(student)) |> 
  ggplot() +
  aes(x = open_total_pomp, y = green_total_pomp, color = factor(student)) +
  geom_point() +
  geom_smooth(method = "lm")

```

```{r graphs/summaries}
green_data |> 
  rowwise() |> 
  summarize(
    mean = mean(l),
    sd = sd(lifeExp)
  )


ggplot(green_data) + 
aes(x = greenrep, y = compassion) +
  geom_point() 
```

## 2. Compute total scores for the four scales. Recode variables as needed.

```{r total scores}

```

## 3.Rescale the variables so that they go from 0-100 instead of the original range. Name the recaled variables *_pomp.

```{r rescale}

```

## 4. Make plots that illustrate the distributions of the 4 POMP-scored variables.

```{r plots}

```

## 5. Make scatterplots showing the relationships between green reputation and each personality trait. Include trend lines for students and non-students. What do these plots show?

```{r personality scatterplots}

```

## 6. Compare green reputation for students and non-students using a rainfall plot (bar + density + data points).

```{r rainfall plot}

```

## 7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.

```{r summary table}

```
