---
title: "Lab 02 - Plastic waste"
author: "Jude Sullivan"
date: "January 27, 2022"
output: html_document
---

## Load packages and data

```{r setup, message=FALSE}
# Load the tidyverse package

library(tidyverse)
```

```{r load-data, message=FALSE}

#install.packages("here")

plastic_waste <- read.csv(here::here("data/plastic-waste.csv"))

```

## Exercises

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.

```{r plastic-waste-continent}

#histograms by continent 

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = 0.2) +
  facet_wrap(~continent)

```

```{r plastic-waste-continent; density}

#density by continent

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_density(binwidth = 0.2) +
  facet_wrap(~continent)

```

```{r plastic-waste-continent; histogram & density}

#histogram & density by continent 

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_density(aes(y = after_stat(count)), binwidth = 0.2) +
  facet_wrap(~continent)

```

```{r plastic-waste-continent; density colored}

#colored density by continent 

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap,
      fill =  continent,
      color = continent) +
  geom_density(binwidth = 0.2) +
  facet_wrap(~continent)

#Per instructions to describe why the placement of "alpha" is important, I believe I used facet wrong and should have overlapping plots by country rather than separate plots for each country... 

```

### Exercise 2

```{r plastic-waste-density; boxplot }

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap,
      fill =  continent,
      color = continent) +
  geom_boxplot(binwidth = 0.2) +
  facet_wrap(~continent)

```

```{r plastic-waste-density; raincloud}

#install.packages("ggdist")

ggplot(data = plastic_waste) +
  aes(y = continent,
      x = plastic_waste_per_cap,
      fill = continent,
      color = continent) +
  geom_jitter(height = .15) +
  geom_boxplot(color = "black",
               alpha = .5,
               width = .1,
               size = .5) +
  ggdist::stat_slab(height = .3,
                    color = "black",
                    size = .2,
                    alpha = .5,
                    position = position_nudge(y = .2))

```

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

```{r plastic-waste-density; scatterplot}

ggplot(data = plastic_waste) +
  aes(y = plastic_waste_per_cap,
      x = mismanaged_plastic_waste_per_cap,
      fill = continent,
      color = continent,
      shape = continent) +
  geom_point()

```

```{r plastic-waste-density; scatterplot w/ population}

#plastic_waste_per_cap x total_pop 

ggplot(data = plastic_waste) +
  aes(y = plastic_waste_per_cap,
      x = total_pop,
      fill = continent,
      color = continent,
      shape = continent) +
  geom_point()

#plastic_waste_per_cap x coastal_pop

ggplot(data = plastic_waste) +
  aes(y = plastic_waste_per_cap,
      x = coastal_pop,
      fill = continent,
      color = continent,
      shape = continent) +
  geom_point()

#upon further investigation, it seems as though the outliers should not be there :O

```



### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements



