---
title: "Lab 4"
author: "Jude Sullivan"
date: "2/10/2022"
output: html_document
---

# In this lab, You will analyze data looking at the relationship between green reputation and three personality traits– compassion, intellectual curiosity, and openness to experiences. The dataset includes data from students and non-students.

```{r setup, include=FALSE}
# Load the tidyverse package

library(tidyverse)
library(dplyr)
```


```{r data}
#import data

dictionary <- readr::read_csv(here::here("data", "green_dictionary.csv"))
green_data <- readr::read_csv(here::here("data", "green_data.csv"))
```

## 1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). Is anything unusual?

```{r graphs/summaries}
#making green reputation composite variable

greenrep <- (green_data c(green1, green2, green3, green4, green5))


green_data |> 
  rowwise() |> 
  mutate(
    id = id,
    greenrep_total = mean(c_across(green1:green5), na.rm = TRUE),
    compassion_total = mean(c_across(comp1:comp10), na.rm = TRUE),
    intelcur_total = mean(c_across(intel1:intel10), na.rm = TRUE),
    open_total = mean(c_across(open1:open10), na.rm = TRUE),
    .before = everything()
  ) |>
  head() 


  
```

```{r graphs/summaries}
green_data |> 
  rowwise() |> 
  summarize(
    mean = mean(l),
    sd = sd(lifeExp)
  )
```

## 2. Compute total scores for the four scales. Recode variables as needed.

```{r total scores}

```

## 3.Rescale the variables so that they go from 0-100 instead of the original range. Name the recaled variables *_pomp.

```{r rescale}

```

## 4. Make plots that illustrate the distributions of the 4 POMP-scored variables.

```{r plots}

```

## 5. Make scatterplots showing the relationships between green reputation and each personality trait. Include trend lines for students and non-students. What do these plots show?

```{r personality scatterplots}

```

## 6. Compare green reputation for students and non-students using a rainfall plot (bar + density + data points).

```{r rainfall plot}

```

## 7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.

```{r summary table}

```
