---
title: "Lab 4"
author: "Jude Sullivan"
date: "2/10/2022"
output: html_document
---

```{r setup, include=FALSE}
# Load the tidyverse package

library(tidyverse)
library(dplyr)
```


```{r data}
#import data

dictionary <- readr::read_csv(here::here("data", "green_dictionary.csv"))
green_data <- readr::read_csv(here::here("data", "green_data.csv"))
```

## 1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). Is anything unusual?

```{r graphs/summaries}

```

## 2. Compute total scores for the four scales. Recode variables as needed.

```{r total scores}

```

## 3.Rescale the variables so that they go from 0-100 instead of the original range. Name the recaled variables *_pomp.

```{r rescale}

```

## 4. Make plots that illustrate the distributions of the 4 POMP-scored variables.

```{r plots}

```

## 5. Make scatterplots showing the relationships between green reputation and each personality trait. Include trend lines for students and non-students. What do these plots show?

```{r personality scatterplots}

```

## 6. Compare green reputation for students and non-students using a rainfall plot (bar + density + data points).

```{r rainfall plot}

```

## 7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.

```{r summary table}

```
