---
title: "Progdata Lab 3"
author: "Jude Sullivan"
date: "2/3/2022"
output: html_document
---

```{r setup, include=FALSE}
#load tidyverse and gapminder packages

library(tidyverse)
library(gapminder)

```


# Exercise 1

## 1.1


```{r country, year}
#I tried to find viable countries by looking at the years in the 1970s that have data; only 1972 and 1977

#Australia, Cuba, Greece

gapminder |> 
  filter(country %in% c("Australia", "Cuba", "Greece") & year %in% c("1972", "1977"))
```

## 1.2

```{r country, year, select gdp}
gapminder |> 
  filter(country %in% c("Australia", "Cuba", "Greece") & year %in% c("1972", "1977")) |> 
  select(country, gdpPercap)
```
## 1.3

```{r country, year, lifeExp}
gapminder |> 
  filter(country %in% c("Australia", "Cuba", "Greece") & year %in% c("1972", "1977")) |> 
  mutate(x = c(lifeExp)) |> 
  arrange(year == 1977, year == 1972)

#the code above creates x in the table but this does not save in order for me to compute the difference, so I am writing out the vector with life expectancies with 1977 - 1972 by writing the life expectancies for Australia, Cuba, and Greece in 1972 followed by their life expectancies in 1977 and then using the lag function to get 1977-1972

x <- c(71.930, 70.723, 72.340, 73.490, 72.649, 73.680)

diff(x, lag = 3)

```

## 1.4

```{r country, year, max gdp}
gapminder |> 
  group_by(country) |> 
   mutate(max_gdp = max(gdpPercap)) 

```

## 1.5

```{r scatterplot, canada, lifeexp, gdp}
gapminder |> 
  filter(country %in% "Canada")

canada <- filter(gapminder, country %in% "Canada")

#without log

ggplot(canada) + 
aes(x = gdpPercap, y = lifeExp) +
  geom_point() 

#with log

ggplot(canada) + 
aes(x = gdpPercap, y = lifeExp) +
  geom_point() + 
  scale_x_log10()

```

# Exercise 2

```{r ex2}
datasets::iris

tibble(iris)

iris_tbl <- as_tibble(iris)

knitr::kable(iris_tbl)

```

## 2.1

```{r summary, scatterplot}
summarize(iris, mean(Sepal.Length), sd(Sepal.Length), range(Sepal.Length), 
          mean(Petal.Length), sd(Petal.Length), range(Petal.Length))

ggplot(iris) +
  aes(x = Sepal.Length, y = Petal.Length) +
  geom_point()

```

##2.2

```{r summary, scatterplot, categorical}
iris |> 
  group_by(Species) |> 
  summarize(n(),mean(Sepal.Length), sd(Sepal.Length), range(Sepal.Length))

ggplot(iris) +
  aes(x = Species, y = Sepal.Length) +
  geom_point()

#scatterplot

ggplot(iris) +
  aes(y = Species,
      fill =  Species,
      color = Species) +
  geom_boxplot(binwidth = 0.2) 

#raincloud plot

ggplot(iris) +
  aes(y = Species,
      x = Sepal.Length,
      fill = Species,
      color = Species) +
  geom_jitter(height = .15) +
  geom_boxplot(color = "black",
               alpha = .5,
               width = .1,
               size = .5) +
  ggdist::stat_slab(height = .3,
                    color = "black",
                    size = .2,
                    alpha = .5,
                    position = position_nudge(y = .2))

```

# Bonus Exercise

Evaluate this code and describe the result. The goal was to get the data for Rwanda and Afghanistan. Does this work? Why or why not? If not, what is the correct way to do this?

filter(gapminder, country == c("Rwanda", "Afghanistan"))

```{r bonus}
knitr::kable(gapminder)

#incorrect
filter(gapminder, country == c("Rwanda", "Afghanistan"))

#correct
filter(gapminder, country %in% c("Rwanda", "Afghanistan"))

```

The discrepancy occurs because Rwanda and Afghanistan are not equal in values, which cut off most of the data from both countries